\Large \bf Library Dialysis with Lya

### 2019-12-21 paper/draft.tex
More work in related work

\section{Applications of Analysis}
\label{apps}

@@

\section{Related Work}
\label{rw}
Some citations to ensure we can see them~\cite{Christophe:2015:DAU:2819009.2819180, Keil:2013:EDA:2508168.2508176, Lehmann:2019:WFD:3297858.3304068, Sun:2018:EDA:3178372.3179527}.

@@

% \section*{Acknowledgments}
% 
% \section*{Availability}

>>>>

% \section{Applications of Analysis}
% \label{apps}

@@

\section{Related Work}
\label{rw}

Existing dynamic analysis frameworks can be classified either as coarse- or fine-grained.
The former analyze interactions at the boundaries of entire components, whereas the latter associate metadata at the level of individual instructions or objects.
We compare \sys to previously proposed systems in both categories, then contrast the two categories' overall characteristics.

\heading{Heavyweight instrumentation}
There is a series of heavyweight dynamic analysis frameworks.
Popular frameworks include
  Valgrind~\cite{valgrind} and Pin~\cite{pin} for native programs,
  DiSL~\cite{disl} and RoadRunner~\cite{roadrunner} for JVM byte code,
  Jalangi~\cite{jalangi} for JavaScript programs, and,
  most recently, Wasabi~\cite{wasabi} for Web-Assembly.

The approach advocated by \sys is to throw a quick-and-easy analysis at the module boundaries

Jalangi is the most relevant of these frameworks, and served as an inspiration

\heading{Dynamic Analysis for WebAssembly}
Related to JavaScript is WebAssembly, a standardized subset of JavaScript target ideal as a compilation target.
Two techniques modify V8

Wasabi is a framework for dynamic analysis of WebAssembly.
Similar to \sys, it succeeds at lowering the effort required to write analyses, 
and provides hooks for observation rather than manipulation
Contrary to \sys, Wasabi instruments binaries statically, \ie ahead-of-time, and aims on heavyweight instrumentation.

; even more similarly, it allows expressing analyses in JavaScript.
Prior work has modified

Some citations to ensure we can see them~\cite{javascript1, javascript2, javascript3}.

\heading{Dynamic Instrumentation}
Dialysis is related to dynamic binary instrumentation frameworks that wrap parts of the program to extract information.
Many such frameworks translate basic blocks of the program just before their execution;
  \sys starts with a phase that wraps (equivalent to instrumenting) a library during import, adding a small overhead at the loading time of each library.
The overhead of this phase is only a small fraction of the time required to locate and load the module from disk.

\heading{Program Transformations}
% Add our work
Module dialysis builds on aspect-oriented programming (AOP), a programming model that maps program points to actions to be taken at these points~\cite{aop}.
Both approaches lower complexity by mapping multiple points across the program to the same actions, but dialysis does not alter the program's control flow.
Moreover, AOP works on languages that were already designed to support it, whereas module dialysis was explicitly designed to bolt onto existing languages and environments.

More generally AOP is related to metaobjects~\cite{metaobject}, objects that manipulate object structure and which enable a program to access to its own internal structure, including rewriting itself as it executes.
They are examples of runtime reflection, of which \sys makes extensive use to traverse, understand, wrap, and rewrite interfaces.
With \sys, however, developers do not need to provide their own metaobjects.
% self element

\heading{Fracture and Recombination}
Module dialysis draws inspiration directly from program fracture and recombination (PFR)~\cite{fracture1, fracture3}, a line of work less tied to program analysis and more towards program synthesis and automated patch generation.
PFR breaks up multiple programs into multiple components (called shards) with the goal of exchanging functionality between donor-donee pairs of programs.
Module dialysis operates on single programs, avoids breaking semantics, and leverages the existence of components with (mostly) explicit boundaries, in the guise of libraries or modules.

@@

Recent trends in software engineering have led to unprecedented levels of third-party code re-use.
Applications today routinely pull together hundreds of libraries, making their analysis difficult

due to the very same abstraction and modularity principles that have benefited software engineering for decades.

security auditing and performance profiling---already challenging in monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.

This paper introduces \emph{module dialysis}, an approach 
corser
approach towards coarse-grained
This is achieved using a set of programmatic \emph{transformations} parametrizable by optional \emph{distribution recipes}.
These operate at module boundaries during runtime to collect profiling information, detect bottlenecked components, and dynamically separate and coalesce parts of the application.

% \section*{Acknowledgments}
% Martin
% \section*{Availability}
